% Created 2017-12-04 Mon 09:39
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{hyperref}
\tolerance=1000
\usepackage[margin=0.5in]{geometry}
\author{Louis Tsiattalou}
\date{\textit{<2017-11-30 Thu>}}
\title{Trade Data Visualisation QA Spec}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs 25.1.1 (Org mode 8.2.10)}}
\begin{document}

\maketitle
This document is intended to be a checklist for the purposes of quality assuring the Trade Data Visualisation web application.

\section{Data Integrity}
\label{sec-1}
\begin{itemize}
\item $\square$ Do the results of the query match up with raw HMRC Trade Data?
\begin{itemize}
\item $\square$ Imports
\item $\square$ Exports
\item $\square$ Dispatches (EU Exports)
\item $\square$ Arrivals (EU Imports)
\end{itemize}
\item $\square$ Do the contents of the comcode table match up with raw HMRC Trade Data and EUROSTAT data?
\item $\square$ Are the Ports and Country alpha codes still correct?
\end{itemize}

\section{Technical}
\label{sec-2}
\begin{itemize}
\item $\square$ Does the app crash when no data is returned from a query?
\item $\square$ Do the Visualisations render correctly?
\begin{itemize}
\item $\square$ Sankey Diagrams
\item $\square$ World Map Visualisation
\item $\square$ Time Series Plots
\begin{itemize}
\item $\square$ Comcode
\item $\square$ Country
\item $\square$ Port
\end{itemize}
\end{itemize}
\end{itemize}

\section{UI}
\label{sec-3}
\begin{itemize}
\item $\square$ Is the performance of the app acceptable?
\item $\square$ Do the Commodity Code Selectors cascade correctly?

\emph{This means, are all the commodity codes displayed in the selectors descendants of those selected in lower-digit fields?}

\item $\square$ Is the Date Range displaying all valid values?
\item $\square$ Is everything reasonably sized on the page?
\item $\square$ When running new queries, do the existing Visualisations grey-out?
\item $\square$ Do the search functions on the Comcode Lookup tab work correctly?
\begin{itemize}
\item $\square$ Fuzzy Search bar at top
\item $\square$ Comcode Search
\item $\square$ Description Search
\end{itemize}
\item $\square$ Are the Comcode Legend entries (above the visualisations) showing \emph{only} the comcodes in play?
\item $\square$ Is the interface of the app intuitive?
\begin{itemize}
\item Please enter any comments on how to improve the interface of the app:
\end{itemize}
\end{itemize}

\vspace*{6cm}

\begin{itemize}
\item Please enter any additional comments and improvements below:
\end{itemize}
% Emacs 25.1.1 (Org mode 8.2.10)
\end{document}
